Dynein walks like an Imperial AT-ST

### 2018-06-29 papers/paper/paper.tex
Add progress on model-cryoem figure script
mini commit
finish up model figure
Fix minor bug in parameters-to-latex script
Make new crystal structure superimposed figure work (sort of) - still needs work

\input{../../data/paper_static_stepping_parameters.tex}

@@

\begin{figure*}[tbhp]
\centering
\includegraphics[width=0.3\linewidth]{figures/onebound-cartoon.pdf}%
\includegraphics[width=0.3\linewidth]{figures/bothbound-cartoon.pdf}%
\includegraphics[width=0.3\linewidth]{figures/schematic-1-superimposed}\\
\includegraphics[width=0.15\linewidth]{../../plots/poststroke-figure.pdf}%
\includegraphics[width=0.15\linewidth]{../../plots/prestroke-figure.pdf}%
\includegraphics[width=0.3\linewidth]{figures/schematic-binding-angle}
\caption{}
\label{fig:duration-length}
\end{figure*}

@@

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & & \cite{nativestructure}\\
$L_t$ & $\lt nm$ & & \cite{nativestructure}\\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\
$D$ & 0.2 nm &  & \\

@@

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Make our cool figures presentable, e.g. trajectory plot.
\item Describe our algorithm in sufficient detail.
\item Ensure our experimental figures have at least one version with
  scale bars.
\item Write script to generate figures with cartoon on top of
  microscopy images.
\item Store our preferred geometric (and non-geometric) parameters in
  a python module, which is used both for creating figures (see above)
  and for running simulations.
\item Python script to write out latex with parameters.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\end{enumerate}

>>>>

\input{../../data/paper_params.tex}

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.49\linewidth]{figures/onebound-cartoon.pdf}%
\includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
\caption{}
\end{figure}

\begin{figure}[tbhp]
\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/redwine-model-figure.pdf}%
\includegraphics[width=0.5\linewidth]{../../plots/chowdhury-model-figure.pdf}\\
\includegraphics[width=0.5\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model superimposed over ---maybe the burgess paper is bad since it uses dynein c, which seems like an axonemal dynein}
\label{fig:duration-length}
\end{figure}

@@

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & & \cite{nativestructure}\\
$L_t$ & $\lt nm$ & & \cite{nativestructure}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\
$D$ & 0.2 nm &  & \\

@@

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Make our cool figures presentable, e.g. trajectory plot.
\item Describe our algorithm in sufficient detail.
\item Ensure our experimental figures have at least one version with
  scale bars.
\item Write script to generate figures with cartoon on top of
  microscopy images.
\item Store our preferred geometric (and non-geometric) parameters in
  a python module, which is used both for creating figures (see above)
  and for running simulations.
\item Python script to write out latex with parameters.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\item Add force-dependent plots to compare with yildiz?
\end{enumerate}
